New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/article.tex
local
label SAT

\subsection{Reformulation as a SAT problem}

@@

\begin{remark}
The performance of
\end{remark}

@@

\par
First

@@

More precisely, we verified the following results using the glucose SAT solver [reference].

>>>>

\subsection{Reformulation as a SAT problem}
\label{SAT}

@@

\begin{remark}
For a given problem, it can be interesting to try out different SAT solvers because the relative performance can vary significantly according to the problem. 
For instance, we used two different SAT solvers in the next two next subsections.
\end{remark}

@@

\par
\hyperlink{label4}{\textbf{[4]}} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of \([\![1,197]\!]\) with  
\(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only assuming \(m_5 = 67\) even after several 
weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5 seconds with the SAT solver glucose 
on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here but in the rest of this subsection, we used the parallel version of glucose). 
The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free subsets starts with a partition of 
\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among the 3 partitions of \([\![1,23]\!]\) in 
3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two different subsets. We hardcoded 
this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation time.

@@

More precisely, we verified the following results.
